%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.5in,top=0.5in,right=0.5in,bottom=0.5in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Miles Turpin} % Your name
\address{(203)~505~5523 \\ miles.turpin@duke.edu \\ \textit{github.com/milesaturpin} \\ \textit{linkedin.com/in/milesaturpin}}

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

\begin{rSubsection}{Duke University}{\em expected May 2020}{}
%\begin{itemize}
\item  B.S. in Data Science, B.S. in Mathematics, Minor in Philosophy --- Cumulative GPA: 3.3
\item  Relevant coursework: {\em High Dimensional Data --- Artificial Intelligence --- Data Science --- Statistics --- Databases --- Algorithms --- Data Structures \& Algorithms --- Advanced Probability ---  Discrete Math  --- Linear Algebra --- Multivariable Calculus --- Complex Systems @ MIT}
\item Spring coursework: {\em Machine Learning (Graduate level) --- Bayesian Statistics}
\item Honors: Judge's Pick at American Statistical Association DataFest at Duke \hfill {Spring 2018}
\end{rSubsection}
%Minor in Linguistics \smallskip \\
%Member of Eta Kappa Nu \\
%Member of Upsilon Pi Epsilon \\

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

\begin{rSubsection}{Carin Research Group, Information Initiative at Duke (iiD)}{June 2018 - Present}{Machine learning researcher}{Duke University}
%\item The Carin Lab at Duke University works on machine learning projects in everything from healthcare to bomb detection. Overseen by Dr. Lawrence Carin, one of the world's most widely-published machine learning researchers.
\item Building machine learning models on time series EHR data to predict likelihood of emergency surgery for patients with a severe stomach complication (SBO), advised by Dr. Lawrence Carin and Dr. Matthew Englehard. \textit{Paper forthcoming}.
\item Compiled the largest and most detailed dataset of SBO patients for analysis.

\end{rSubsection}

\begin{rSubsection}{Future of Humanity Institute, University of Oxford}{May 2018 - Sept 2018}{Machine learning researcher}{}
%\item The Future of Humanity Institute is a multidisciplinary research institute at the University of Oxford that uses the tools of mathematics, philosophy and social sciences to bear on big-picture questions about humanity and its prospects.
\item Used machine learning to identify lab-specific signatures of engineered DNA to predict its lab-of-origin. \textit{Paper forthcoming -- Plasmid Attribution: Toward Accountability in Genetic Engineering}.
\item Beat the state-of-the-art by 20 points (68\% accuracy).
\item Leveraged AWS for parallel web scraping and model training
\end{rSubsection}


\begin{rSubsection}{Industry Activity by US Metropolitan Area}{April 2018}{Judge's Pick}{Duke University}
\item Identified industry hotspots across US metropolitan areas using job posting data from Indeed; see Github.
\item Awarded Judge's Pick at American Statistical Association DataFest at Duke. Competed against over 400 students, over half of which were Master's students.
\end{rSubsection}

\begin{rSubsection}{Effective Altruism: Duke}{Spring 2017 - Present}{President}{Duke University}
%\item Effective Altruism: Duke directs exceptional Duke undergraduates and graduates to consequential career paths in  global poverty, artificial intelligence safety, biosecurity, and more.
\item Created and currently run the first iteration of the Arete Fellowship, a selective program offering an accelerated introduction to Effective Altruism for students who are motivated to think rationally about how to have a significant positive impact on the world. See \textit{eaduke.org/faq}.
\item Coordinated activities resulting in 9 people taking the Giving What We Can pledge (donating 10\% of future income to effective charities).
\end{rSubsection}

\end{rSection}


%	AWARDS SECTION
%----------------------------------------------------------------------------------------

% \begin{rSection}{Awards} \itemsep -2pt
% \begin{rSubsection}{American Statistical Association DataFest}{April 2018}{Winner}{Duke University}
% \item Identified industry hotspots across US metropolitan areas using job posting data from Indeed; see Github.
% \item Competed against over 400 students, over half of which were Master's students.
% \end{rSubsection}
% \end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Programming Languages &  Python, R, SQL, Scheme \\
Software \& Packages & Tensorflow, Scikit-learn, Pandas, Numpy, Git, Tableau \\
\end{tabular}

\end{rSection}


%----------------------------------------------------------------------------------------


\begin{rSection}{ACTIVITIES}


\begin{rSubsection}{Philosophy Society}{Spring 2017 - Present}{Exec Member}{Duke University}
\item Organized a discussion between two prominent  philosophers on the existence of God, attended by 100+ students.
\end{rSubsection}




\begin{rSubsection}{Duke Triathlon}{Fall 2017 - Present}{}{}
\item Completed an Ironman 70.3 in Patagonia in March 2018.
\end{rSubsection}

%\textbf{Jazz piano and music production}


\end{rSection}

\end{document}
