%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.5in,top=0.5in,right=0.5in,bottom=0.5in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Miles Turpin} % Your name
\address{(203)~505~5523 \\ miles.turpin@duke.edu \\ \textit{github.com/milesaturpin} \\ \textit{linkedin.com/in/milesaturpin}}

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

\begin{rSubsection}{Duke University}{\em expected May 2020}{}
%\begin{itemize}
\item  B.S. in Data Science, B.S. in Mathematics, Minor in Philosophy --- Cumulative GPA: 3.3
\item  Relevant coursework: {\em High Dimensional Data --- Artificial Intelligence --- Data Science --- Statistics --- Databases --- Algorithms --- Data Structures \& Algorithms --- Advanced Probability ---  Discrete Math  --- Linear Algebra --- Multivariable Calculus --- Complex Systems @ MIT}
\item Spring coursework: {\em Machine Learning (Graduate level) --- Bayesian Statistics}

\end{rSubsection}

\begin{rSubsection}{Honors}{}{}{}
	\item \textit{Best Insight} at American Statistical Association DataFest at Duke \hfill {April 2019}
		\begin{list}{$\cdot$}{\leftmargin=2em}\itemsep -0.5em \vspace{-0.5em}
			\item Built personalized models for each player on the Canadian National Women's Rugby Team to understand each individual's predictors of fatigue over the course of the season; see Github. Competed against over 400 students.
		\end{list}
	\item \textit{Judge's Pick} at American Statistical Association DataFest at Duke \hfill {April 2018}
	\begin{list}{$\cdot$}{\leftmargin=2em}\itemsep -0.5em \vspace{-0.5em}
			\item Identified industry hotspots across US metropolitan areas using job posting data from Indeed; see Github. Competed against over 400 students.
		\end{list}

\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Research Experience}

\begin{rSubsection}{IBM Research Cambridge, Learning Health Systems}{Starting May 2019}{Incoming machine learning researcher}{Cambridge, Boston}
	\item Will be working on applying deep learning to healthcare applications.
\end{rSubsection}

\begin{rSubsection}{Carin Research Group, Information Initiative at Duke (iiD)}{June 2018 - Present}{Machine learning researcher}{Duke University}
\item Building machine learning models on time series EHR data to predict likelihood of emergency surgery for patients with a severe stomach complication (SBO), advised by Dr. Lawrence Carin and Dr. Matthew Englehard. \textit{Paper forthcoming}.
\item Compiled the largest and most detailed dataset of SBO patients for analysis.
\end{rSubsection}

\begin{rSubsection}{Future of Humanity Institute, Oxford University}{June 2018 - Sept 2018}{Machine learning researcher}{}
\item Used machine learning to identify lab-specific signatures of engineered DNA to predict its lab-of-origin. \textit{Paper forthcoming -- Plasmid Attribution: Toward Accountability in Genetic Engineering}.
\item Beat the state-of-the-art by 20 points (68\% accuracy).
\item Leveraged AWS for parallel web scraping and model training
\end{rSubsection}

% \begin{rSubsection}{Industry Activity by US Metropolitan Area}{April 2018}{Judge's Pick}{Duke University}
% \item Identified industry hotspots across US metropolitan areas using job posting data from Indeed; see Github.
% \item Awarded Judge's Pick at American Statistical Association DataFest at Duke. Competed against over 400 students, over half of which were Master's students.
% \end{rSubsection}

\end{rSection}


%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Programming Languages &  Python, R, SQL, Scheme \\
Software \& Packages & Tensorflow, Scikit-learn, Pandas, Numpy, Matplotlib, Git, Tableau \\
\end{tabular}

\end{rSection}


%----------------------------------------------------------------------------------------


\begin{rSection}{ACTIVITIES \& LEADERSHIP}

\begin{rSubsection}{Effective Altruism: Duke}{Spring 2017 - Present}{President}{Duke University}
\item Created and currently run the first iteration of the Arete Fellowship, a selective program offering an accelerated introduction to Effective Altruism for students who are motivated to think rationally about how to have a significant positive impact on the world. See \textit{eaduke.org/faq}.
% \item Coordinated activities resulting in 9 people taking the Giving What We Can pledge (donating 10\% of future income to effective charities).
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Duke Philosophy Society}{Spring 2017 - Present}{}{}
\item Organized a discussion between two prominent  philosophers on the existence of God, attended by 100+ students
\end{rSubsection}

\begin{rSubsection}{Duke Triathlon}{Fall 2017 - Present}{}{}
\item Completed an Ironman 70.3 in Patagonia in March 2018
\end{rSubsection}

%\textbf{Jazz piano and music production}


\end{rSection}

\end{document}
